\documentclass{main}
\usepackage[margin=0.7in]{geometry}
\usepackage{enumitem}
\usepackage{multicol}
\usepackage{xcolor}

\renewcommand\thefootnote{\textcolor{black}{\arabic{footnote}}}

\newcommand{\updateinfo}[1][\today]{\par\vfill\hfill{\scriptsize\color{gray}Last updated on #1}}
\setlist[itemize]{leftmargin=*}

\name{FENGYU LI}
\address{\href{mailto:fl334@cornell.edu}{\color{black}fl334@cornell.edu} \\ \href{https://fengyuli.com/}{\color{black}fengyuli.com}}

\begin{document}

\begin{rSection}{Education}
    {\bf Cornell University} \hfill {Aug 2021 - May 2025}\\
    B.A. in Computer Science \& B.A. in Mathematics \hfill \textit{Ithaca, NY} \\
    GPA: 4.086 / 4.3
\end{rSection}

\begin{rSection}{Publications}
    In progress.

\end{rSection}

\begin{rSection}{Research Experience}
    \vspace{0.1em}
    \textbf{College of Computing and Information Science, Cornell University} \hfill Feb 2022 - Present\\
    \textit{Research Assistant} \hfill \textit{Ithaca, NY}
    \begin{itemize}
        \itemsep -3pt {}
        \item \textbf{In Progress, advised by Prof. Sanjiban Choudhury} \\
        In progress.
        \item \textbf{In Progress, advised by Prof. Sarah Dean} \\
              In progress.
        \item \textbf{Document-level Information Extraction, at Cornell NLP Group} \\
              Learned about recent progress in deep learning and information extraction. Reproduced results of DyGIE++, a pretrained transformer model, on multiple datasets.
    \end{itemize}
    % \textbf{Cornell University Artificial Intelligence} \hfill Sep 2022 - Present\\
    % \textit{Undergraduate Researcher} \hfill \textit{Ithaca, NY}
    % \begin{itemize}
    %     \itemsep -3pt {}
    %     \item \textbf{In Progress} \\
    % \end{itemize}
\end{rSection}

\begin{rSection}{Awards \& Recognitions}
    \begin{itemize}[noitemsep]
        \item Cornell CSURP Grant for Undergraduate Research
        \item Cornell Research Assistant Stipend
        \item Dean's List, Cornell University
        \item Best Project Award, Cornell Honors Data Structures Course
        \item Team Lead of China, Silver Medal, International Economics Olympiad 2020
    \end{itemize}
\end{rSection}

\begin{rSection}{Activities \& Services}
    \vspace{-1em}
    \item \textbf{\textit{Software Developer,} Cornell Design \& Tech Initiative} \hfill Oct 2021 - May 2022
    \vspace{-0.4em}
    \begin{itemize}
        \itemsep -0.4em {}
        \item Built a cross-platform web application that provides ride scheduling for students with disabilities.
    \end{itemize}
\end{rSection}

\begin{rSection}{Teaching}
    \begin{itemize}[noitemsep]
        % \item \textit{Teaching Assistant,} CS 4780 Machine Learning for Intelligent Systems \hfill{Fall 2022}
        \item \textit{Teaching Assistant,} CS 4780 Machine Learning for Intelligent Systems \hfill{Fall 2022}
        \item \textit{Teaching Assistant,} CS 2110 Object-Oriented Programming and Data Structures \hfill{Spring 2022}
    \end{itemize}
\end{rSection}

\begin{rSection}{Coursework}
    \vspace{-0.5em}
    \begin{multicols}{2}
        \textbf{Undergraduate-level Courses}
        \vspace{-0.2em}
        \begin{itemize}[noitemsep]
            \item Machine Learning
            \item Analysis of  Algorithms
            \item Reinforcement Learning
            \item Deep Learning for Computer Vision
            \item Honors Mathematics Sequence (In Progress) {\color{red}\footnote{Honors advanced algebra, analysis, and measure-theoretic probability theory}}
        \end{itemize}
        \columnbreak
        \textbf{Graduate/PhD-level Courses}
        \vspace{-0.2em}
        \begin{itemize}[noitemsep]
            \item Machine Learning Theory
            \item RL Theory (Planned)
        \end{itemize}
    \end{multicols}
    \vspace{-1.4em}
\end{rSection}

\end{document}
